Article Title

### 2018-01-23 doc/letter_editor.tex
rejected from bjls. reformatted for peerj

\begin{document}
\begin{letter}{Editor \\ \textit{Systematic Biology}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration at the journal \textit{Systematic Biology}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.

@@

  An earlier version of this manuscript was submitted and subsequently rejected with an encouragement to resubmit (USYB-2015-207). Since this decision this study has undergone substatial revisions, the inclusion of new analysis, and is overall considerably different from the manuscript submitted in 2015. Because of these major chnages and the resubmission option expiring in October 2016, we are resubmitting this manuscript as a new article.

>>>>

\begin{document}
\begin{letter}{Editor \\ \textit{Biological Journal of the Linnean Society}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration for the \textit{Biological Journal of the Linnean Society}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.

@@

  %An earlier version of this manuscript was submitted and subsequently rejected with an encouragement to resubmit (USYB-2015-207). Since this decision this study has undergone substatial revisions, the inclusion of new analysis, and is overall considerably different from the manuscript submitted in 2015. Because of these major chnages and the resubmission option expiring in October 2016, we are resubmitting this manuscript as a new article.
